Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-29 main.tex

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{{\it more...}}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for 
%mm 
    multi-channel 
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy 
%mm through 
    by
galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal 
%mm + 
   and
power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in 
%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

>>>>

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Benoit C{\^o}t{\'e}}
\affiliation{T.B.D.}
\author{Kathryn V. Johnston}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{Brian O'Shea}
\affiliation{T.B.D.}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for
%mm
    multi-channel
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy
%mm through
    by
galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal
%mm +
   and
power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in
%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}
